|

### 2020-05-18 paper/Manuscript.Rmd
updatesss

The functionality of 'Git' is amplified by services such as 'GitHub'
(https://github.com; other similar services include 'GitLab', https://gitlab.com
and 'Bitbucket', https://bitbucket.org). 'GitHub' is best understood as a cloud
storage service with social networking functionality. The cloud storage aspect
of 'GitHub' works as follows: You can "clone" (copy) a local 'Git' repository to
the 'GitHub' website, as a backup or research archive. The social network aspect
comes into play when a repository on 'GitHub' is set to "public": This allows 
other researchers to peruse the repository and see how the work was done, clone
it to their own computer to replicate the original work or apply the methods to
their own data, open "Issues" to ask questions or give feedback on the project,
or even send a "Pull request" with suggested changes to the text or code for
your consideration. 'Git' and 'GitHub' shine as tools for collaboration, because
different people can simultaneously work on different parts of a project, and
their changes can be compared and automatically merged on the website. Even on
solo projects, working with 'Git'/'GitHub' has many benefits: Staying organized,
being able to start a new study with a clone of an old, similar repository, or
splitting off an "experimental branch" to try something new, while retaining the
ability to revert to a previous state of the project, or to merge the 
experimental branch.

The third solution is *dependency management*: Keeping track of exactly what software was used to conduct the analyses. <!-- Being able to replicate analyses requires not only access to the data and analysis code, but also to the software used to evaluate that code.--> At first glance, it might seem sufficient to state that analyses were conducted in *Program X*. However, every program is susceptible to changes and updates. R-packages in particular are updated frequently, because they are Open Source, and there is an active community of developers contributing functionality and bugfixes. Potentially, any update could change the results of the code. For example, R-version 3.6.0 fixed a bug in the random number generator. This means that any analyses that use random numbers, such as bootstrapping, cannot be strictly replicated from previous versions. Or, for example, R-version 4.0.0 changed a default parameter that affects how data are loaded from files.

>>>>

The functionality of 'Git' is amplified by services such as 'GitHub'
(https://github.com. 'GitHub' is best understood as a cloud
storage service with social networking functionality. The cloud storage aspect
of 'GitHub' works as follows: You can "clone" (copy) a local 'Git' repository to
the 'GitHub' website, as a backup or research archive. The social network aspect
comes into play when a repository on 'GitHub' is set to "public": This allows 
other researchers to peruse the repository and see how the work was done, clone
it to their own computer to replicate the original work or apply the methods to
their own data, open "Issues" to ask questions or give feedback on the project,
or even send a "Pull request" with suggested changes to the text or code for
your consideration. 'Git' and 'GitHub' shine as tools for collaboration, because
different people can simultaneously work on different parts of a project, and
their changes can be compared and automatically merged on the website. Even on
solo projects, working with 'Git'/'GitHub' has many benefits: Staying organized,
being able to start a new study with a clone of an old, similar repository, or
splitting off an "experimental branch" to try something new, while retaining the
ability to "revert" (return) to a previous state of the project, or to "merge"
(incorporate) the experimental branch. Although this paper focuses on 'GitHub',
`worcs` (as of version 0.1.2) supports alternative services such as 'GitLab'
(https://gitlab.com) and 'Bitbucket' (https://bitbucket.org), and has a vignette
detailing instructions for these platforms.

The third solution is *dependency management*: Keeping track of exactly what
software was used to conduct the analyses. At first glance, it might seem
sufficient to state that analyses were conducted in *Program X*. However, every
program is susceptible to changes, updates, and bugfixes. R-packages in
particular are updated frequently, because they are Open Source, and there is an
active community of developers contributing functionality and bugfixes. 
Potentially, any update could change the results of the code. For example, 
R-version 3.6.0 fixed a bug in the random number generator. This means that any
analyses that use random numbers, such as bootstrapping, cannot be strictly
replicated from previous versions. Or, for example, R-version 4.0.0 changed a
default parameter that affects how data are loaded from files.
